Measuring contrast processing in the visual system using SSVEP

### 2024-04-20 review.qmd
Suppress code output

---
title: "Measuring contrast processing in the visual system using SSVEP"
author:
  - name: Alex R. Wade
  - name: Daniel H. Baker
format: 
  pdf:
    keep-tex: true
bibliography: WadeBaker_Review.bib
csl: visual-neuroscience.csl
execute:
  echo: false
---
Department of Psychology and York Biomedical Research Institute, University of York, UK

@@

axs[0].plot(support_S, inputModulation)
axs[0].set_title('Input sine wave', fontsize=10)

@@

axs[0].plot(support_S, transducedModulation)
axs[0].set_title('Transduced signal', fontsize=10)

@@

![Linear.](Figures/linearsystem.pdf){#fig-linear}

![Linear.](Figures/transducer.pdf){#fig-transducer}

![Linear.](Figures/twoinputs.pdf){#fig-twoinputs}

>>>>

---
title: "Measuring contrast processing in the visual system using SSVEP"
author:
  - name: Alex R. Wade
  - name: Daniel H. Baker
format: 
  pdf:
    keep-tex: true
bibliography: WadeBaker_Review.bib
csl: visual-neuroscience.csl
execute:
  echo: false
  output: false
  include: false
---
Department of Psychology and York Biomedical Research Institute, University of York, UK

@@

axs[0].plot(support_S, inputModulation)
axs[0].set_title('Input sine wave', fontsize=10)
axs[0].set_xlabel('Time (s)')

@@

axs[0].plot(support_S, transducedModulation)
axs[0].set_title('Transduced signal', fontsize=10)
axs[0].set_xlabel('Time (s)')

@@

![Linear](Figures/linearsystem.pdf){#fig-linear}

![Nonliner](Figures/transducer.pdf){#fig-transducer}

![Two inputs](Figures/twoinputs.pdf){#fig-twoinputs}
